Supplementary material for ``Screening Sinkhorn Algorithm for Regularized Optimal Transport''

### 2019-05-22 tex/v3/section_5_numeric_expes.tex
running time

We compare \emph{Screenkhorn} to Sinkhorn as implemented in POT toolbox\footnote{\url{https://pot.readthedocs.io/en/stable/index.html}} on  a synthetic example. The dataset we use consists of source samples generated from a bi-dimensional gaussian mixture and target samples following the same distribution but with different gaussian means. We consider an unsupervised domain adaptation using optimal transport with entropic regularization.  Several settings are explored: different values of $\eta$, the regularization parameter, the allowed budget $\frac{n_b}{n} = \frac{m_b}{m} = $ ranging from $0.01$ to $0.99$, different values of $n$ and $m$.
% and, whether the cost matrix $C$ is normalized or not.
 We empirically measure  marginal violations as the norms $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$, running time expressed as $\frac{T_{\text{\emph{Screenkhorn}}}}{T_{\text{Sinkhorn}}}$ and the relative divergence difference $| \inr{C, P^\star} - \inr{C, P^{\text{sc}}}|/\inr{C, P^\star}$ between \emph{Screenkhorn} and Sinkhorn, where $P^\star = \Delta(e^{u^\star}) K \Delta(e^{v^\star})$ and $P^{\text{sc}} = \Delta(e^{u^{\text{sc}}}) K \Delta(e^{v^{\text{sc}}}).$
Figure \ref{fig:margin_expe} summarizes the observed behaviors of both algorithms under these settings. We choose to only report results for $n=m=1000$ as we get similar findings for other values of $n$ and $m$.

>>>>

We compare \emph{Screenkhorn} to Sinkhorn as implemented in POT toolbox\footnote{\url{https://pot.readthedocs.io/en/stable/index.html}} on  a synthetic example. The dataset we use consists of source samples generated from a bi-dimensional gaussian mixture and target samples following the same distribution but with different gaussian means. We consider an unsupervised domain adaptation using optimal transport with entropic regularization.  Several settings are explored: different values of $\eta$, the regularization parameter, the allowed budget $\frac{n_b}{n} = \frac{m_b}{m} = $ ranging from $0.01$ to $0.99$, different values of $n$ and $m$.
% and, whether the cost matrix $C$ is normalized or not.
 We empirically measure  marginal violations as the norms $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$, running time expressed as $\frac{T_{\text{Sinkhorn}}}{T_{\text{\emph{Screenkhorn}}}}$ and the relative divergence difference $| \inr{C, P^\star} - \inr{C, P^{\text{sc}}}|/\inr{C, P^\star}$ between \emph{Screenkhorn} and Sinkhorn, where $P^\star = \Delta(e^{u^\star}) K \Delta(e^{v^\star})$ and $P^{\text{sc}} = \Delta(e^{u^{\text{sc}}}) K \Delta(e^{v^{\text{sc}}}).$
Figure \ref{fig:margin_expe} summarizes the observed behaviors of both algorithms under these settings. We choose to only report results for $n=m=1000$ as we get similar findings for other values of $n$ and $m$.
